---
title: "Scenaton2020"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    runtime: shiny
    vertical_layout: scroll
---


<style>
.body{
background-color:#2B6974;
}
.navbar {
  background-color:#94B046;
}

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
    background-color: #2B6974;
    color: white;
}
.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: white;
  background-color: #2B6974;
}
.navbar-inverse .navbar-toggle:hover,
.navbar-inverse .navbar-toggle:focus {
  background-color: #2B6974;
}
.navbar-inverse .navbar-collapse,
.navbar-inverse .navbar-form {
  border-color: #2B6974;
}

.h3{
font-size:40px;
}


</style>


```{r global, include=FALSE}
library(shiny)
library(ggplot2)
library(readr)
library(plotly)
ALL_ROW_REGIONS <- read_csv("all_row_regions.csv")
ALL_FABLE_COUNTRIES <- read_csv("all_fable_countries.csv")
COUNTRIE_REGION <- read_csv("countries_regions.csv")
```


```{r setup, include=FALSE}
library(flexdashboard)
```


Net Forest Cover Change 
=======================================================

Column {.sidebar}
-------------------------------------
```{r}

selectInput("graficaType",
                        "tipo de grafica:",
                        choice=list("Group","all row regions","all fable countries"))
```
 
Column
-------------------------------------
    
### Net Forest Cover Change
    
```{r}



renderPlotly({

        if(input$graficaType=="all row regions")
        {
          
         grafica_1<-ggplot(data=ALL_ROW_REGIONS,aes(x=Year,y=net_forest_change))+
            geom_bar(stat = "identity", fill="#FFC107",width=3)+
            geom_point(aes(x=Year,y=GFW_deforestation))+theme_classic()+
            geom_point(aes(x=Year,y=forest_target),colour="red")+
            geom_point(aes(x=Year,y=net_forest_change),colour="green")+scale_y_continuous(breaks=seq(0, -17500, -2500)) #Marcas del 0 al -17500, cada -2500.  
         b<-ggplotly(grafica_1)
         b
      
        }else if(input$graficaType=="all fable countries")
        {
          grafica_2<-ggplot(data=ALL_FABLE_COUNTRIES,aes(x=Year,y=aforestation))+
            geom_bar(stat = "identity", fill="#81C784",width=3)+
            geom_bar(aes(x=Year,y=forest_loss),stat = "identity", fill="#FFC107",width=3)+theme_classic()+
            geom_point(aes(x=Year,y=net_forest_change),colour="green")+
            geom_point(aes(x=Year,y=GFW_deforestation))+
            geom_point(aes(x=Year,y=forest_target),colour="red")+scale_y_continuous(breaks=seq(60000, -30000, -20000))
          a<-ggplotly(grafica_2)
          a
        }else if(input$graficaType=="Group")
        {
          grafico_3<-ggplot(data=COUNTRIE_REGION,aes(x=Year,y=aforestation))+
  geom_bar(stat = "identity", fill="#81C784",width=3)+
  geom_bar(aes(x=Year,y=forest_loss),stat = "identity", fill="#FFC107",width=3)+theme_classic()+
  geom_point(aes(x=Year,y=net_forest_change),colour="green")+
  geom_point(aes(x=Year,y=GFW_deforestation))+
  geom_point(aes(x=Year,y=forest_target),colour="red")

grafico_3+scale_y_continuous(breaks=seq(60000, -40000, -20000))

ggplotly(grafico_3)
        }
        
      

    })

```
    

asdasd


Biodiversity
=========================================
Column 
-----------------------------------------------------------------------

### Chart A

```{r}


```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```
